### 2013-09-04 rscripts/manuscript.tex
manuscript components

\begin{document}
\SweaveOpts{concordance=TRUE}
\begin{flushleft}
{\Large
\textbf{Detecting Covert Groups Embedded in a Population}
}
% Insert Author names, affiliations and corresponding author email.
\\
Carl A. B. Pearson$^{1,\ast}$, 
Edo Airoldi$^{2}$, 
Edward Kao$^{2}$,
Burton Singer$^{1}$, 
\\
\bf{1} Emerging Pathogens Institute, University of Florida, Gainesville, FL, USA
\\
\bf{2} Statistics, Harvard University, Cambridge, MA, USA
\\
$\ast$ E-mail: cap10@ufl.edu
\end{flushleft}
% Please keep the abstract between 250 and 300 words
\section*{Abstract}
We outline the problem of characterizing strategies for detection and concealment of clandestine coordination within a broader population, in terms of network models.  Specifically, we propose means to accommodate the uncertainty about behavior and capability from both ends, a general plan for developing such models, some best practices for model parameterization and data gathering, and finally some particularly pernicious pitfalls.

@@

@recursive def cliqueGroups(col: Collection[Collection[V]], size:Int) =
  val thisLvl : Collection[Collection[V]] =
    // gather the groups being made into a higher level cliques
    for ( subGroups <- groupBySize(col, size) ) yield {
      // clique a group of groups
      for ( (leftGroup, rightGroup) <- undirectedPairs(subGroup) ) {
        leftGroup.randomMember <~> rightGroup.randomMember
      }
      // merge this set of subgroups into a single new group
      merge(subGroups)
    }
  // repeat with the cliqued cliques, unless everything has been connected
  if (thisLvl.size != 1) cliqueGroups(thisLvl, size)  
\end{code}

@@

<<readInCliqued,echo=FALSE>>=
library(igraph)
pree <- read.table("../1-EL.txt",col.names=c("sender_id","recipient_id","type"))
pree[which(pree[,1]<0),1] <- -pree[which(pree[,1]<0),1]
pree[which(pree[,2]<0),2] <- -pree[which(pree[,2]<0),2]
edgeinfo <- t(pree)
# hack: doesn't seem reasonable to have sim output other vertex labels
#edgeinfo[1,which(edgeinfo[1,] == 107)] <- 103
#edgeinfo[2,which(edgeinfo[2,] == 107)] <- 103
#edgeinfo[1,which(edgeinfo[1,] == 112)] <- 104
#edgeinfo[2,which(edgeinfo[2,] == 112)] <- 104

gWhole <- graph(edgeinfo[-3,])
V(gWhole)$size<-2
V(gWhole)[c(102,103,104)]$size<-6
E(gWhole)[which(edgeinfo[3,]=="Work")]$color <- "green"
E(gWhole)[which(edgeinfo[3,]=="Work")]$weight <- 0.1
E(gWhole)[which(edgeinfo[3,]=="Family")]$color <- "blue"
E(gWhole)[which(edgeinfo[3,]=="Family")]$weight <- 0.1
E(gWhole)[which(edgeinfo[3,]=="Religion")]$color <- "purple"
E(gWhole)[which(edgeinfo[3,]=="Plot")]$color <- "red"
#gAlt <- delete.vertices(gWhole, which(degree(gWhole) < 1)-1)
l<-layout.auto(gWhole)
@

\begin{rnwfig}
<<all, fig=TRUE, width=7.5, echo=FALSE>>=
plot(gWhole, edge.arrow.size=0.01, edge.color="grey", vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{Overlay of all connections; the large vertex represents the cluster of subordinates.}
\end{rnwfig}

\begin{rnwfig}
<<religion, fig=TRUE, width=7.5, echo=FALSE>>=
E(gWhole)[which(edgeinfo[3,]=="Work")]$color <- NA
E(gWhole)[which(edgeinfo[3,]=="Family")]$color <- NA
plot(gWhole, edge.arrow.size=0.01, vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{The same graph, showing the plot connections (red) and religious (purple) links.}
\end{rnwfig}

\begin{rnwfig}
<<work, fig=TRUE, width=7.5, echo=FALSE>>=
E(gWhole)[which(edgeinfo[3,]=="Work")]$color <- "green"
E(gWhole)[which(edgeinfo[3,]=="Religion")]$color <- NA
plot(gWhole, edge.arrow.size=0.01, vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{Now showing work (green) links.}
\end{rnwfig}

\begin{rnwfig}
<<family, fig=TRUE, width=7.5, echo=FALSE>>=
E(gWhole)[which(edgeinfo[3,]=="Family")]$color <- "blue"
E(gWhole)[which(edgeinfo[3,]=="Work")]$color <- NA
plot(gWhole, edge.arrow.size=0.01, vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{Now showing family (blue) links.}
\end{rnwfig}

@@

<<readInTree,echo=FALSE>>=
pree <- read.table("../1-EL-alt.txt",col.names=c("sender_id","recipient_id","type"))
pree[which(pree[,1]<0),1] <- -pree[which(pree[,1]<0),1]
pree[which(pree[,2]<0),2] <- -pree[which(pree[,2]<0),2]
edgeinfo <- t(pree)

gWholeAlt <- graph(edgeinfo[-3,])
V(gWholeAlt)$size<-2
V(gWholeAlt)[c(102,103,104)]$size<-6
E(gWholeAlt)[which(edgeinfo[3,]=="Work")]$color <- "green"
E(gWholeAlt)[which(edgeinfo[3,]=="Work")]$weight <- 0.1
E(gWholeAlt)[which(edgeinfo[3,]=="Family")]$color <- "blue"
E(gWholeAlt)[which(edgeinfo[3,]=="Family")]$weight <- 0.1
E(gWholeAlt)[which(edgeinfo[3,]=="Religion")]$color <- "purple"
E(gWholeAlt)[which(edgeinfo[3,]=="Plot")]$color <- "red"
l<-layout.auto(gWholeAlt)
@

\begin{rnwfig}
<<allAlt, fig=TRUE, width=7.5, echo=FALSE>>=
plot(gWholeAlt, edge.arrow.size=0.01, edge.color="grey", vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{Overlay of all connections; again, the large vertex represents the cluster of subordinates.}
\end{rnwfig}

\begin{rnwfig}
<<religionAlt, fig=TRUE, width=7.5, echo=FALSE>>=
E(gWholeAlt)[which(edgeinfo[3,]=="Work")]$color <- NA
E(gWholeAlt)[which(edgeinfo[3,]=="Family")]$color <- NA
plot(gWholeAlt, edge.arrow.size=0.01, vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{The same graph, showing the plot connections (red) and religious (purple) links.}
\end{rnwfig}

\begin{rnwfig}
<<workAlt, fig=TRUE, width=7.5, echo=FALSE>>=
E(gWholeAlt)[which(edgeinfo[3,]=="Work")]$color <- "green"
E(gWholeAlt)[which(edgeinfo[3,]=="Religion")]$color <- NA
plot(gWholeAlt, edge.arrow.size=0.01, vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{Now showing work (green) links.}
\end{rnwfig}

\begin{rnwfig}
<<familyAlt, fig=TRUE, width=7.5, echo=FALSE>>=
E(gWholeAlt)[which(edgeinfo[3,]=="Family")]$color <- "blue"
E(gWholeAlt)[which(edgeinfo[3,]=="Work")]$color <- NA
plot(gWholeAlt, edge.arrow.size=0.01, vertex.label=NA, vertex.frame.color=NA, layout=l)
@
\caption{Now showing family (blue) links.}
\end{rnwfig}

@@

<<preRes,echo=FALSE>>=
structureFiles <- sort(list.files("..","structure_\\d+\\.txt"))
contentFiles <- sort(list.files("..","content_\\d+\\.txt"))
sandcFiles <- sort(list.files("..","sandc_\\d+\\.txt"))
badFiles <- sort(list.files("..","bad_\\d+\\.txt"))
astructureFiles <- sort(list.files("..","astructure_\\d+\\.txt"))
acontentFiles <- sort(list.files("..","acontent_\\d+\\.txt"))
asandcFiles <- sort(list.files("..","asandc_\\d+\\.txt"))
abadFiles <- sort(list.files("..","abad_\\d+\\.txt"))
popsize <- 100
plotsize <- 6

qData<-function(src) {
  FPR<-sapply(src,function(fname) {
    read.table(paste("../",fname,sep=""),header=F,sep=" ",col.names=c("FPR","TPR"))$FPR
  },simplify="matrix") / popsize
  FPRq <- apply(FPR,1,quantile)
  TPR<-sapply(src,function(fname) {
    read.table(paste("../",fname,sep=""),header=F,sep=" ",col.names=c("FPR","TPR"))$TPR
  },simplify="matrix") / plotsize
  TPRq <- apply(TPR,1,quantile)
  list(TPRq=TPRq,FPRq=FPRq)
}
sQData <- qData(structureFiles)
sFPRq <- sQData$FPRq
sTPRq <- sQData$TPRq
asQData <- qData(astructureFiles)
asFPRq <- asQData$FPRq
asTPRq <- asQData$TPRq

cQData <- qData(contentFiles)
cFPRq <- cQData$FPRq
cTPRq <- cQData$TPRq
acQData <- qData(acontentFiles)
acFPRq <- acQData$FPRq
acTPRq <- acQData$TPRq

sandcQData <- qData(sandcFiles)
sandcFPRq <- sandcQData$FPRq
sandcTPRq <- sandcQData$TPRq
asandcQData <- qData(asandcFiles)
asandcFPRq <- asandcQData$FPRq
asandcTPRq <- asandcQData$TPRq

badMR <- sapply(badFiles,function(fname) {
  read.table(paste("../",fname,sep=""),header=F,col.names=c("badMR"))$badMR
},simplify="matrix")
badMR <- badMR / max(badMR)
badMRq <- apply(badMR,1,quantile)

abadMR <- sapply(abadFiles,function(fname) {
  read.table(paste("../",fname,sep=""),header=F,col.names=c("badMR"))$badMR
},simplify="matrix")
abadMR <- abadMR / max(abadMR)
abadMRq <- apply(abadMR,1,quantile)

timesteps <- 100
samples <- 100
t<-1:timesteps
tm <- matrix(t,nrow=timesteps,ncol=samples)
backpoly<-function(t,x,color,lb=0) {
  polygon( c(min(t), t, max(t)), c( lb, x, lb), col=color, border=NA )
}
liner<-function(t,TPRq,FPRq,TPRxy,FPRxy) {
  lines(x=t,y=TPRq[3,],col="green3",type="l",xlab="iterate",ylab="FPR",ylim=c(0,1))
  lines(x=t,y=TPRq[4,],col="darkolivegreen1")
  lines(x=t,y=TPRq[2,],col="darkolivegreen1")
  lines(x=t,y=FPRq[3,],col="red")
  lines(x=t,y=FPRq[4,],col="coral")
  lines(x=t,y=FPRq[2,],col="coral")
  text(TPRxy[1],TPRxy[2],"TPR",col="green3")
  text(FPRxy[1],FPRxy[2],"FPR",col="red")
}
plotter<-function(t,badMRq,TPRq,FPRq,TPRxy,FPRxy) {
  plot(t,badMRq[5,],type="l",col="grey93",ylab="",xlab="",yaxt="n",xaxt="n",bty="n")
  backpoly(t,badMRq[5,],col="grey93")
  backpoly(t,badMRq[4,],col="grey85")
  backpoly(t,badMRq[2,],col="grey93")
  backpoly(t,badMRq[1,],col="white",lb=-1)
  axis(side=1,at=c(min(t),max(t)),labels=c(expression(t[min]),expression(t[max])),tick=F,line=-1)
  text(75,0.5,"MR")
  liner(t,TPRq,FPRq,TPRxy,FPRxy)
}
@
\subsection*{Structural Performance}
\begin{rnwfig}
<<structure, fig=TRUE, width=7.5, echo=FALSE>>=
plotter(t,badMRq,sTPRq,sFPRq,c(20,0.5),c(80,.15))
@
\caption{Structure-Only performance versus clique-based background.}
\end{rnwfig}

\begin{rnwfig}
<<astructure, fig=TRUE, width=7.5, echo=FALSE>>=
plotter(t,abadMRq,asTPRq,asFPRq,c(20,0.5),c(80,.15))
@
\caption{Structure-Only performance versus tree-based background.}
\end{rnwfig}

\begin{rnwfig}
<<content, fig=TRUE, width=7.5, echo=FALSE>>=
plotter(t,badMRq,cTPRq,cFPRq,c(20,0.5),c(80,.15))
@
\caption{Content-Only performance versus clique-based background.}
\end{rnwfig}

\begin{rnwfig}
<<acontent, fig=TRUE, width=7.5, echo=FALSE>>=
plotter(t,abadMRq,acTPRq,acFPRq,c(20,0.5),c(80,.15))
@
\caption{Content-Only performance versus tree-based background.}
\end{rnwfig}

\begin{rnwfig}
<<sandcontent, fig=TRUE, width=7.5, echo=FALSE>>=
plotter(t,badMRq,sandcTPRq,sandcFPRq,c(20,0.5),c(80,.15))
@
\caption{Structure and Content performance versus clique-based background.}
\end{rnwfig}

\begin{rnwfig}
<<asandcontent, fig=TRUE, width=7.5, echo=FALSE>>=
plotter(t,abadMRq,asandcTPRq,asandcFPRq,c(20,0.5),c(80,.15))
@
\caption{Structure and Content performance versus clique-based background.}
\end{rnwfig}

>>>>

\usepackage{Sweave}
\begin{document}
\input{manuscript-concordance}
\begin{flushleft}
{\Large
\textbf{Detecting Covert Groups Embedded in a Population}
}
% Insert Author names, affiliations and corresponding author email.
\\
Carl A. B. Pearson$^{1,\ast}$, 
Edo Airoldi$^{2}$, 
Edward Kao$^{2}$,
Burton Singer$^{1}$, 
\\
\bf{1} Emerging Pathogens Institute, University of Florida, Gainesville, FL, USA
\\
\bf{2} Statistics, Harvard University, Cambridge, MA, USA
\\
$\ast$ E-mail: cap10@ufl.edu
\end{flushleft}
% Please keep the abstract between 250 and 300 words
\section*{Abstract}
We outline the problem of characterizing strategies for detection and concealment of clandestine coordination within a broader population, in terms of network models.  Specifically, we propose means to accommodate the uncertainty about behavior and capability from both ends, a general plan for developing such models, some best practices for model parameterization and data gathering, and finally some particularly pernicious pitfalls.

@@

  val thisLvl : Collection[Collection[V]] =
    // gather the groups being made into a higher level cliques
    for ( subGroups <- groupBySize(col, size) ) yield {
      // clique a group of groups
      for ( (leftGroup, rightGroup) <- undirectedPairs(subGroup) ) {
        leftGroup.randomMember <~> rightGroup.randomMember
      }
      // merge this set of subgroups into a single new group
      merge(subGroups)
    }
  // repeat with the cliqued cliques, unless everything has been connected
  if (thisLvl.size != 1) cliqueGroups(thisLvl, size)  
\end{code}

@@

\begin{rnwfig}
\includegraphics{manuscript-all}
\caption{Overlay of all connections; the large vertex represents the cluster of subordinates.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-religion}
\caption{The same graph, showing the plot connections (red) and religious (purple) links.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-work}
\caption{Now showing work (green) links.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-family}
\caption{Now showing family (blue) links.}
\end{rnwfig}

@@

\begin{rnwfig}
\includegraphics{manuscript-allAlt}
\caption{Overlay of all connections; again, the large vertex represents the cluster of subordinates.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-religionAlt}
\caption{The same graph, showing the plot connections (red) and religious (purple) links.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-workAlt}
\caption{Now showing work (green) links.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-familyAlt}
\caption{Now showing family (blue) links.}
\end{rnwfig}

@@

\subsection*{Structural Performance}
\begin{rnwfig}
\includegraphics{manuscript-structure}
\caption{Structure-Only performance versus clique-based background.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-astructure}
\caption{Structure-Only performance versus tree-based background.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-content}
\caption{Content-Only performance versus clique-based background.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-acontent}
\caption{Content-Only performance versus tree-based background.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-sandcontent}
\caption{Structure and Content performance versus clique-based background.}
\end{rnwfig}

\begin{rnwfig}
\includegraphics{manuscript-asandcontent}
\caption{Structure and Content performance versus clique-based background.}
\end{rnwfig}
